Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-08-12 man/figures/gc_perc_trees.Rmd
improve figures

```{r data}
gc_treesMed <- read.csv(here("data/disturbance", "disturbance_trees_gc_treshold_median.csv"), header = TRUE, sep = ',')
gc_treesMed50 <- read.csv(here("data/disturbance", "disturbance_trees_gc_treshold_median50.csv"), header = TRUE, sep = ',')
```

@@

label_site <- c("0_sj" = "SJ",
                "1_caH" = "CA-High",
                "2_caL" = "CA-Low")

>>>>

```{r data}
gc_treesMed <- read.csv(here("data/disturbance", "disturbance_trees_gc_treshold_median.csv"), header = TRUE, sep = ',')
gc_treesMed50 <- read.csv(here("data/disturbance", "disturbance_trees_gc_treshold_median50.csv"), header = TRUE, sep = ',')

gc_treesMed50 <- gc_treesMed50 %>% mutate(site_sorted = 
                                recode_factor(site,
                                              "gc_caH" = "0_caH", 
                                              "gc_caL" = "1_caL", "gc_sj" = "2_sj"))

label_site <- c("2_sj" = "SJ",
                "0_caH" = "CA-High",
                "1_caL" = "CA-Low")

@@

### 2019-08-12 man/figures/residual_chronos.Rmd
update legend
improve figures

@@

```{r plot_rwi}
label_site <- c("0_sj" = "SJ",
                "1_caH" = "CA-High",
                "2_caL" = "CA-Low")

cro_rwi <- cro_rwi %>% 
  mutate(siteF = case_when(
    site_sorted == "0_sj" ~ "Northern (SJ)",
    site_sorted == "1_caH" ~ "Southern (Ca-High)",
    site_sorted == "2_caL" ~ "Southern (Ca-Low)"))

# 
plot_rwi_crono <- ggplot(cro_rwi, aes(x=year, y=res)) +
  theme_bw() + 
  theme(panel.grid = element_blank(), 
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face="bold", size=9), 
        # strip.text = element_blank(), 
        axis.text = element_text(size=8), 
        axis.title = element_text(face="bold", size=9)) + 
  geom_hline(yintercept = 1, colour = "grey") + 
  geom_line(size=.8) + scale_y_continuous(breaks = seq(0.4,1.8, 0.2)) +
  facet_wrap(~site_sorted, scales = "free_x", ncol = 1,
             labeller = as_labeller(label_site)) + 
  ylab("Ring width index") + xlab("Year") + 
  geom_vline(aes(xintercept = year), data = year_cutoffs,  linetype = "dashed", colour='red') + 
  # geom_vline(aes(xintercept = year), data = year_sampledepth,  linetype = "dashed", colour='blue') +
  geom_vline(xintercept = dys, linetype = "dotted") + 
  # geom_vline(xintercept = dys, linetype = "dotted") + 
  scale_x_continuous(limits = c(1819, 2016), 
                     breaks= seq(1820, 2020, by=20))

@@

**Figure S3.** Residual tree-ring chronologies obtained for the *Q. pyrenaica* sites. Dashed red lines indicate the start of the reliable period (EPS > 0.85). Dotted black lines showing the severe drought years identified in our climatic data (see Table S3).

>>>>

# Reorder 
cro_rwi <- cro_rwi %>% mutate(site_sorted = 
                                recode_factor(site,
                                              "caH" = "0_caH", 
                                              "caL" = "1_caL", "sj" = "2_sj"))

year_cutoffs <- year_cutoffs %>% mutate(site_sorted = 
                                recode_factor(site,
                                              "caH" = "0_caH", 
                                              "caL" = "1_caL", "sj" = "2_sj"))

year_sampledepth <- year_sampledepth %>% mutate(site_sorted = 
                                   recode_factor(site,
                                              "caH" = "0_caH", 
                                              "caL" = "1_caL", "sj" = "2_sj"))

@@

```{r plot_rwi}

label_site <- c("2_sj" = "SJ",
                "0_caH" = "CA-High",
                "1_caL" = "CA-Low")

# 
plot_rwi_crono <- ggplot(cro_rwi, aes(x=year, y=res, colour=site)) +
  theme_bw() + 
  theme(panel.grid = element_blank(), 
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face="bold", size=9), 
        # strip.text = element_blank(), 
        axis.text = element_text(size=8), 
        axis.title = element_text(face="bold", size=9), 
        legend.position = "none") + 
  geom_hline(yintercept = 1, colour = "grey") + 
  geom_line(size=.8) + scale_y_continuous(breaks = seq(0.4,1.8, 0.2)) +
  facet_wrap(~site_sorted, scales = "free_x", ncol = 1,
             labeller = as_labeller(label_site)) + 
  ylab("Ring width index") + xlab("Year") + 
  geom_vline(aes(xintercept = year), data = year_cutoffs,  linetype = "dashed", colour='red') + 
  # geom_vline(aes(xintercept = year), data = year_sampledepth,  linetype = "dashed", colour='blue') +
  geom_vline(xintercept = dys, linetype = "dotted") + 
  # geom_vline(xintercept = dys, linetype = "dotted") + 
  scale_x_continuous(limits = c(1819, 2016), 
                     breaks= seq(1820, 2020, by=20)) +
  scale_colour_manual(values = colores_den)

@@

**Figure S3.** Residual tree-ring chronologies obtained for the *Q. pyrenaica* sites. Dashed red lines indicate the start of the reliable period (EPS > 0.85). Dotted black lines showing the severe drought years identified in our climatic data (Table S3 and Figure S1).
